|

### 2023-02-06 paper.Rmd
Mon Feb  6 18:02:44 CET 2023: update-remote.sh

The framework that was used to run all experiments of this thesis was provided by the supervisor of this thesis David Wittenberg and uses the python programming language [@python3] in conjunction with the baseline libraries `Keras` [@chollet2015keras] for deep neural networks and `deap` [@DEAP_JMLR2012] for evolutionary computation. For data visualizations I used the python package `matplotlib` [@matplotlib], statistical analysis and evaluations were conducted using primarily the datscience libraries `numpy` [@numpy], `pandas` [@pandas], and

@@

The first interesting observation from this experiment is, that the pre-trained DAE-GP shows slightly lower mean RMSE (higher fitness) but a higher median RMSE (lower fitness) than regular DAE-GP for both the training and the testing set in overall fitness. Regarding the presence of overfitting, both DAE-GP variants show only a very small gap between the testing and training fitness which indicates a good generalization behavior.

@@

# II - Statutory Declaration {.unnumbered #IV}

>>>>

The framework that was used to run all experiments of this thesis was provided by the supervisor of this thesis David Wittenberg and uses the python programming language [@python3] in conjunction with the baseline libraries `Keras` [@chollet2015keras] for deep neural networks and `deap` [@DEAP_JMLR2012] for evolutionary computation. For data visualizations I used the python package `matplotlib` [@matplotlib], statistical analysis and evaluations were conducted using primarily the data science libraries `scipy` [@scipy], `numpy` [@numpy], `pandas` [@pandas], and  `IPython` [@ipython].

@@

The first interesting observation from this experiment is, that the pre-trained DAE-GP shows slightly lower mean RMSE (higher fitness) but a higher median RMSE (lower fitness) than regular DAE-GP for both the training and the testing set in overall fitness. Regarding the presence of overfitting, both DAE-GP variants show only a very small gap between the testing and training fitness which indicates a good generalization behavior. Another interesting observation from figure \@ref(fig:airfoil-median-fitness-30gens) is that pre-trained DAE-GP is faster at improving fitness than regular DAE-GP, this is especially true if only looking at the first 10 generations

@@

# Statutory Declaration {.unnumbered #IV}
